A Comparision of Bootstrap Methods

### 2022-12-02 project/PaperTemplate/paper.Rmd
Added some text for simualtion

```{r}
mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
```

@@

```{r}
a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
```

@@

We can use the following to get our studentized confidence interval:
```{r}
mean(~ Dec, data = SnowGR) + qt(c(0.025, 0.975), df = (nrow(SnowGR-1))) * 
  sd(~ Dec, data = SnowGR) / sqrt(nrow(SnowGR))
```

@@

#nboot <- 10000

@@

@@

  # find BCa interval
  theta <- function(x){mean(x)}
  jackknife_results <- bootstrap::jackknife(sampleinput$X, theta)
  jackmean <- mean(~ jackknife_results$jack.values)
  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)

  # find studentized
  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower_q <- t_q[1]
  upper_q <- t_q[2]
  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))

@@

@@

@@

@@

```{r collect data gamma}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 50
 # sim_reps <- 10
  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_gamma, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

@@

  log_normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, "BCa" = V5, "Studentized" = V6) 
  log_normal_output
}

@@

```{r, cache = TRUE}
set.seed(495)
gamma_data1 <- collect_data_gamma(10000)
normal_data1 <- collect_data_normal(10000)
log_normal_data1 <- collect_data_log_normal(10000)
beta_data1 <- collect_data_beta(10000)

write.csv(gamma_data,"gamma_data1_10000.csv", row.names = FALSE)
write.csv(normal_data,"normal_data1_10000.csv", row.names = FALSE)
write.csv(log_normal_data,"log_normal1_data_10000.csv", row.names = FALSE)
write.csv(beta_data,"beta_data1_10000.csv", row.names = FALSE)

@@

```{r}
  gamma_data1 <- gamma_data5 %>%
    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

@@

```{r}
  gamma_data1 <- log_normal_data7 %>%
    pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

```{r, eval = FALSE}
# way with boot library
library(boot)
set.seed(495)

reps <- 2000
n <- 50

X <- rnorm(n, 0, 1)
values <- data.frame(X)

mean.fun <- function(d, i) {
  d <- X[i]
  return (c(mean(d), sd(d)))
}

results <- boot(data = values, statistic = mean.fun, R = reps)

results

plot(results)

ci <- boot.ci(results, type = "all")
ci

>>>>

```{r}
mean(~ Dec, data = SnowGR) + qnorm(c(0.025, 0.975)) * 
  sd(~ Dec, data = SnowGR)/sqrt(nrow(SnowGR))
```

@@

```{r}
a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
                    (1-estimated_a*(z0 + qnorm(alphalow)))); #a_newlow
a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
                     (1-estimated_a*(z0 + qnorm(alphahigh)))); #a_newhigh
qdata(~ mean, c(a_newlow, a_newhigh), data = dec_means)
```

@@

Following the process above, we can use the following to get our studentized confidence interval:

@@

@@

For the simulation, we will randomly sample from distributions in which we know the true population mean. For example, we will sampling from a Gamma Distribution where we can find the true population mean using the shape and rate parameters of the sample distribution. After we sample from a distribution, we will create a bootstrapped confidence interval for each of the methods we described in the exposition. Since we know the true population mean of the distribution, we will determine if the true population parameter is contained in the confidence interval for each of the methods. We will perform this process a large number of times (10,000) and then average by the number of iterations to determine the average proportion that each bootstrapped confidence interval method contains the true population mean. We will do this for a couple different distributions as well as a range of sample sizes show how the intervals perform with skewed distributions and larger sample sizes.

First, we create a function that calculates the bootstrapped confidence intervals from a given sample. To do this, we first bootstrap the sample and then perform each method.

@@

  # find BCa interval
  theta <- function(x){mean(x)}
  jackknife_results <- bootstrap::jackknife(sampleinput$X, theta)
  jackmean <- mean(~ jackknife_results$jack.values)
  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/
                      (1-estimated_a*(z0 + qnorm(alphalow))))
  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/
                       (1-estimated_a*(z0 + qnorm(alphahigh))))
  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)

  # find studentized interval
  t_q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower_q <- t_q[1]
  upper_q <- t_q[2]
  t_interval <- c(sample_mean - (upper_q*sample_se), sample_mean - (lower_q*sample_se))

@@

Next, we will create the simulation that picks the random sample from a distribution and tests to see if the sample creates bootstrapped confidence intervals that contain the true population parameter. First, we have the simulation of selecting from a Normal Distribution. Since we have a $N(0,1)$ distribution, out true population mean is 0.

Second, we select from a Gamma Distribution with a shape parameter of 1 and a scale parameter of 4. This means the true population parameter is 4.

@@

Third, we sample from a Log-Normal distribution with mean log of 0 and a mean standard deviation of 1. Therefore, the true population mean of this distribution is $e^{\frac{1}{2}}$.

@@

Lastly, we sample from a Beta distribution with shape parameters of 4 and 1 which gives us a true population mean of 0.8.

@@

After that, these functions will compile all of the information we have created from the previous methods and run the simulations of each method for a variety of sample sizes.

```{r collect data gamma}
collect_data_gamma <- function(sim_reps) {
  data2 <- matrix(nrow = 5, ncol = 6)
  sample_sizes = 50
  for (i in 1:5) {
    simulation_rep <- seq(1,sim_reps)
    results <- mclapply(simulation_rep, run_simulation_gamma, mc.cores = detectCores())
    df <- data.frame(matrix(unlist(results), nrow=length(results), byrow=TRUE))
    ci_prop <- unname(colSums(df)/sim_reps)

@@

  log_normal_output <- as.data.frame(data2) %>% 
    rename("Sample_Size" = V1, "Standard" = V2, "Percentile" = V3, "BC" = V4, 
           "BCa" = V5, "Studentized" = V6) 
  log_normal_output
}
```

@@

```{r, cache = TRUE, eval = FALSE}
set.seed(495)
gamma_data1 <- collect_data_gamma(10000)
write.csv(gamma_data1,"gamma_data1_10000.csv", row.names = FALSE)

normal_data1 <- collect_data_normal(10000)
write.csv(normal_data1,"normal_data1_10000.csv", row.names = FALSE)

log_normal_data1 <- collect_data_log_normal(10000)
write.csv(log_normal_data1,"log_normal1_data_10000.csv", row.names = FALSE)

beta_data1 <- collect_data_beta(10000)
write.csv(beta_data1,"beta_data1_10000.csv", row.names = FALSE)

@@

```{r, eval = FALSE}
    gamma_data1 <- gamma_data5 %>%
      pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

@@
